Blowing in the wind: Pollution and agricultural productivity in India^[I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on 

### 2023-04-07 draft/draft.Rmd
changes to draft, analyses, and cleaning

---
title: "Blowing in the wind: Pollution and agricultural productivity in India^[I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent Pollution is a growing problem in many developing countries. Using the rollout of coal plants to identify high-pollution locations in India and random variation induced by changes in wind direction, I show that pollution has large, negative impacts on agricultural productivity. Results indicate that some of this impact is driven by changes in labor allocation patterns in response to increased exposure to pollution. I also show that pollution from coal plants, specifically, has a larger effect on agricultural productivity than other types of pollution.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

@@

library(sf)
library(sp)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(ggpubr)
library(ggthemes)
library(rticles)
library(stats)
library(broom)
library(extrafont)
library(fixest)
library(modelsummary)
library(openxlsx)
library(raster)
loadfonts()  # Must be run once in each session (markdown is a new "session" each time you render/knit)

@@

# Tables
plantresultstable <- readRDS("pollution_development/draft/tables/plantresultstable.rds")
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yield1reducedform <- readRDS("pollution_development/draft/tables/yield1reducedform.rds")
yield2naive <- readRDS("pollution_development/draft/tables/yield2naive.rds")
yield3ivmain <- readRDS("pollution_development/draft/tables/yield3ivmain.rds")
yield4monthly <- readRDS("pollution_development/draft/tables/yield4monthly.rds")
yield5heterogeneity <- readRDS("pollution_development/draft/tables/yield5heterogeneity.rds")
yield6leads <- readRDS("pollution_development/draft/tables/yield6leads.rds")
yield7ivdiffindiff <- readRDS("pollution_development/draft/tables/yield7ivdiffindiff.rds")
labor1all <- readRDS("pollution_development/draft/tables/labor1all.rds")
labor2rural <- readRDS("pollution_development/draft/tables/labor2rural.rds")
labor3month <- readRDS("pollution_development/draft/tables/labor3month.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")
monthplot <- readRDS("pollution_development/draft/tables/monthplot.rds")
opplot <- readRDS("pollution_development/draft/tables/opplot.rds")

@@

@@

# Table
colnames(plantresultstable) <- c("1991", "2001", "2001", "2011")
kable(
      plantresultstable, caption = "Local characteristics and the construction of coal plants",
      align = "cccc", booktabs = TRUE, linesep = "", escape = FALSE
      ) %>%
  footnote(
           "Note: Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE,
           escape = FALSE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "1991 census" = 2, "2001 census" = 2)) %>%
  kable_classic_2()

@@

# Table
colnames(yield1reducedform) <- c("(1)", "(2)", "(3)")
kable(
      yield1reducedform, caption = "Wind direction and agricultural productivity",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2.5cm") %>%
  row_spec(13, bold = TRUE) %>%
  row_spec(15, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield2naive) <- c("(1)", "(2)", "(3)")
kable(
      yield2naive, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2.5cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)")
rownames(yield3ivmain)[8] <- "F (first stage)"
kable(
      yield3ivmain, caption = "Pollution and agricultural productivity, IV estimates",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield5heterogeneity) <- c(">p(50)", "<=p(50)", ">p(50)", "<=p(50)", "")
rownames(yield5heterogeneity)[c(1, 3)] <- c("PM 2.5", "PM times rain")
kable(
      yield5heterogeneity, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4.5cm") %>%
  column_spec(c(2:6),width = "1.8cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  add_header_above(c(" " = 1, "wind" = 2, "yield" = 2, " " = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(labor1all) <- c("all", "all", "self", "wage", "farm", "non-farm")
colnames(labor2rural) <- c("all", "all", "self", "wage", "farm", "non-farm")

mat1 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat1) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat1) <- c("panel a: all")
mat2 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat2) <- c("all", "all", "self", "wage", "farm", "non-farm")
rownames(mat2) <- c("panel b: rural")

labortablerural <- rbind(mat1, labor1all[c(1:2, 7:8),], mat2, labor2rural[-c(3:6),], labor2rural[c(3:6),])

@@

# Table
colnames(labor3month) <- c("farm", "non-farm")
kable(
      labor3month, caption = "Wind and labor allocation, by month",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in column one is .  * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(18), hline_after = TRUE) %>%
  row_spec(c(16), bold = TRUE) %>%
  kable_classic_2()

@@

I perform a similar exercise with yield, the results of which are in Table \@ref(tab:yield4monthly). I include only the five months of the year that are used in the calculation of the yield estimates, or June through October. The results are again from two-stage least squares, with the F-statistics for each month presented at the bottom; monthly wind remains a strong predictor of pollution. Column one presents results without controls for weather while column two presents results with controls for weather; the differences in coefficients make clear how important the inclusion of weather is here.

@@

```{r yield4monthly, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Table
colnames(yield4monthly) <- c("(1)", "(2)")
kable(
      yield4monthly, caption = "Pollution and productivity, by month",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(12, bold = TRUE) %>%
  row_spec(14, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

A final caveat about these month-specific results is that they do not take into account possible interactions between different months. For example, yield might respond strongly to average pollution in June and July, which would not be captured in Table \@ref(tab:yield4monthly).

@@

# Table
colnames(yield7ivdiffindiff) <- c("(1)", "(2)", "(3)")
kable(
      yield7ivdiffindiff, caption = "Agricultural productivity and pollution source",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(c(7), bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  kable_classic_2()

@@

data <- matrix(NA, nrow = 8, ncol = 3)
rownames(data) <- c("shapefile", "coal plants", "wind", "pollution", "agriculture", "nightlights", "weather", "labor")
colnames(data) <- c("source", "geographic coverage", "temporal coverage")
data[1,1] <- "Asher et al. (2021)"
data[2,1] <- "Global Energy Monitor"
data[3,1] <- "NCAR"
data[4,1] <- "Hammer et al. (2020)"
data[5,1] <- "Gangopadhya et al. (2022)"
data[6,1] <- "Asher et al. (2021)"
data[7,1] <- "TerraClimate"
data[8,1] <- "National Sample Survey (NSS)"
data[1,2] <- "India"
data[2,2] <- "global"
data[3,2] <- "global"
data[4,2] <- "global"
data[5,2] <- "India"
data[6,2] <- "India"
data[7,2] <- "global"
data[8,2] <- "India"
data[1,3] <- " "
data[2,3] <- "yearly"
data[3,3] <- "daily"
data[4,3] <- "monthly"
data[5,3] <- "two seasons/year"
data[6,3] <- "yearly"
data[7,3] <- "monthly"
data[8,3] <- "daily interviews"

@@

plant1 <- ggplot() +
                theme_map() +
                geom_sf(data = india_shape2, fill = NA, lwd = 0.01) +
                geom_sf(data = plants1990, size = 0.75, color = "black") +
                labs(x = "lon",
                     y = "lat",
                     subtitle = "Figure A: 1990")

plant2 <- ggplot() +
                theme_map() +
                geom_sf(data = india_shape2, fill = NA, lwd = 0.01) +
                geom_sf(data = plants2010, size = 0.75, color = "black") +
                labs(x = "lon",
                     y = "lat",
                     subtitle = "Figure B: 2010")

@@

p1 <- ggplot() + 
        theme_map() +
        geom_sf(data = india_shape, fill = NA) +
        geom_tile(data = windexample, aes(x = x, y = y, fill = wind_example), alpha = 0.3) +
        scale_fill_viridis_c("wind direction\n(degrees)", option = "viridis") +
        geom_sf(data = plants2010, size = 0.5) +
        labs(x = "lon",
             y = "lat",
             subtitle = "Figure A: Wind direction") +
        theme(legend.position = c(0.6, 0.05),
              legend.direction = "vertical",
              legend.key.height = unit(0.4, 'cm'),
              legend.text = element_text(size = 8),
              legend.background=element_blank() )

p2 <- ggplot() + 
        theme_map() +
        geom_sf(data = districts, fill = NA) +
        geom_sf(data = villages %>% filter(is.na(days_sum)==F), aes(fill = days_sum), lwd = NA) +
        scale_fill_viridis_c("exposure (days)", option = "viridis") +
        labs(x = "lon",
             y = "lat",
             subtitle = "Figure B: Aggregation to district") +
        theme(legend.position = c(0.5, 0.05),
              legend.direction = "horizontal",
              legend.key.width = unit(0.3, 'cm'),
              legend.text = element_text(size = 8),
              legend.background=element_blank() )

@@

# Table
colnames(yield6leads) <- c("(1)", "(2)", "(3)")
kable(
      yield6leads, caption = "Agricultural productivity and pollution leads",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(c(9), hline_after = TRUE) %>%
  row_spec(c(7), bold = TRUE) %>%
  kable_classic_2()

>>>>

---
title: "Blowing in the wind: Pollution and agricultural productivity in India^[I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent Pollution is a growing problem in many developing countries. Using the rollout of coal plants to identify high-pollution locations in India and random variation induced by changes in wind direction, I show that pollution has large, negative impacts on agricultural productivity. Results indicate that some of this impact is driven by changes in labor allocation patterns in response to increased exposure to pollution. I also show that pollution from coal plants, specifically, has a larger effect on agricultural productivity than other types of pollution.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

@@

library(sf)
library(sp)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(kableExtra)
library(ggpubr)
library(ggthemes)
library(rticles)
library(stats)
library(broom)
library(extrafont)
library(fixest)
library(modelsummary)
library(openxlsx)
library(raster)
library(viridis)
loadfonts()  # Must be run once in each session (markdown is a new "session" each time you render/knit)

@@

# Tables
plantresultstable <- readRDS("pollution_development/draft/tables/plantresultstable.rds")
pollutiontable <- readRDS("pollution_development/draft/tables/pollutiontable.rds")
yield1reducedform <- readRDS("pollution_development/draft/tables/yield1reducedform.rds")
yield2naive <- readRDS("pollution_development/draft/tables/yield2naive.rds")
yield3ivmain <- readRDS("pollution_development/draft/tables/yield3ivmain.rds")
yield3ivmain_lead <- readRDS("pollution_development/draft/tables/yield3ivmain_lead.rds")
yield4monthly <- readRDS("pollution_development/draft/tables/yield4monthly.rds")
yield5heterogeneity <- readRDS("pollution_development/draft/tables/yield5heterogeneity.rds")
yield6leads <- readRDS("pollution_development/draft/tables/yield6leads.rds")
yield7ivdiffindiff <- readRDS("pollution_development/draft/tables/yield7ivdiffindiff.rds")
labor1all <- readRDS("pollution_development/draft/tables/labor1all.rds")
labor2rural <- readRDS("pollution_development/draft/tables/labor2rural.rds")
labor3month <- readRDS("pollution_development/draft/tables/labor3month.rds")
laborplot <- readRDS("pollution_development/draft/tables/laborplot.rds")
monthplot <- readRDS("pollution_development/draft/tables/monthplot.rds")
opplot <- readRDS("pollution_development/draft/tables/opplot.rds")
coef_vec <- readRDS("pollution_development/draft/tables/randomization_coef_vec.rds")
coefs_distfe <- readRDS("pollution_development/draft/tables/randomization_coefs_distfe.rds")
true_value <- readRDS("pollution_development/draft/tables/randomization_true_value.rds")

@@

@sanders2022adaptation

@@

# Table
colnames(plantresultstable) <- c("1991", "2001", "2001", "2011")
rownames(plantresultstable) <- c("Population (log)", "", "Area (log)", "", "Literacy (prop)", "", "Ag. productivity", "", 
                                "Sub-sample", "Observations")
kable(
      plantresultstable, caption = "Local characteristics and the construction of coal plants",
      align = "cccc", booktabs = TRUE, linesep = "", escape = FALSE
      ) %>%
  footnote(
           "Note: Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01",
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE,
           escape = FALSE
           ) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(9, hline_after = TRUE) %>%
  add_header_above(c(" ", "1991 census" = 2, "2001 census" = 2)) %>%
  kable_classic_2()

@@

# Table
colnames(yield1reducedform) <- c("(1)", "(2)", "(3)")

rownames(yield1reducedform) <- c("Wind days", " ", "Rain (z)", "", "Mean temperature (10s)", "",
                                  "Rain squared", " ", "Temperature squared", " ", "Rain times Temperature", " ",
                                  "Fixed effects:", "Village", "Year",
                                  "Observations")
kable(
      yield1reducedform, caption = "Wind direction and agricultural productivity",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:4),width = "2.5cm") %>%
  row_spec(13, bold = TRUE) %>%
  row_spec(15, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield2naive) <- c("(1)", "(2)", "(3)")
rownames(yield2naive) <- c("Particulate matter", "(log PM 2.5)", 
                           "Weather", "Weather (expanded)",
                           "Fixed effects:", "Village", "Year",
                           "Observations")
kable(
      yield2naive, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:4),width = "2.5cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
yield3ivmain <- yield3ivmain[,-1]
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)")
rownames(yield3ivmain) <- c("Particulate matter", "(log PM 2.5)",
                            "Weather", "Weather (expanded)",
                            "Fixed effects:", "Village", "Year",
                            "F (first stage)", 
                            "Observations")
kable(
      yield3ivmain, caption = "Pollution and agricultural productivity, IV estimates",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(5, bold = TRUE) %>%
  row_spec(7, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

## Robustness checks

```{r randomplot, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.cap = "Randomization inference", fig.footer = list("Note: The figure presents the distribution of coefficients by randomly assigning wind direction across villages within the same year. The \"all\" distribution is created by randomly assigning a single wind value to each village, sampled with replacement across all villages in a given year. The \"within district\" randomly samples with replacement only from within the same district in the same year.")}

pal <- viridis(4)
colors <- c(paste0(pal[1]), paste0(pal[2]))
labels <- c("All", "Within district")

# plot
gg1 <- ggplot() + 
        geom_density(aes(x = coef_vec, fill = "All"), alpha = 0.5) +
        geom_density(aes(x = coefs_distfe, fill = "Within district"), alpha = 0.5) +
        scale_fill_manual(
          name = "Randomization:",
          values = colors,
          labels = labels
        ) +
        theme_minimal() +
        xlab("Distribution of coefficients") +
        ylab("Density")

colors <- c(paste0(pal[3]))
labels <- c("actual")

gg1 <- gg1 + 
        geom_vline(aes(xintercept = true_value, color = "actual")) +
        scale_color_manual(
          name = "",
          values = colors,
          labels = labels
        ) +
        theme(legend.position = c(0.4, 0.6))

gg1

# Table
colnames(yield3ivmain_lead) <- c("(1)", "(2)")
rownames(yield3ivmain_lead) <- c("Particulate matter", "(log PM 2.5)",
                                 "Particulate matter", "(one-year lead)",
                                 "Weather",
                                 "Fixed effects:", "Village", "Year",
                                 "F (current)", "F (lead)", 
                                 "Observations")
kable(
      yield3ivmain_lead, caption = "Agricultural productivity and pollution leads",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(yield5heterogeneity) <- c(">p(50)", "<=p(50)", ">p(50)", "<=p(50)", "")
rownames(yield5heterogeneity)[c(1, 3)] <- c("PM 2.5", "PM times rain")
rownames(yield5heterogeneity) <- c("Particulate matter", "(log PM 2.5)", "PM times Rain", "", "Weather",
                                   "Fixed effects:", "Village", "Year", 
                                   "F (1st stage, PM)", "F (1st stage, PM times rain)", 
                                   "Observations")
kable(
      yield5heterogeneity, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4.5cm") %>%
  column_spec(c(2:6),width = "1.8cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  add_header_above(c(" " = 1, "Wind" = 2, "Yield" = 2, " " = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(labor1all) <- c("All", "All", "Self", "Wage", "Farm", "Non-farm")
colnames(labor2rural) <- c("All", "All", "Self", "Wage", "Farm", "Non-farm")

mat1 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat1) <- c("All", "All", "Self", "Wage", "Farm", "Non-farm")
rownames(mat1) <- c("Panel A: all")
mat2 <- matrix(c("", "", "", "", "", ""), nrow = 1)
colnames(mat2) <- c("All", "All", "Self", "Wage", "Farm", "Non-farm")
rownames(mat2) <- c("Panel B: Rural")

labortablerural <- rbind(mat1, labor1all[c(1:2, 7:8),], mat2, labor2rural[-c(3:6),], labor2rural[c(3:6),])
rownames(labortablerural)[c(2,7)] <- "Wind"
rownames(labortablerural)[c(5,10)] <- "Observations"
rownames(labortablerural)[11] <- "Controls"
rownames(labortablerural)[12] <- "Fixed effects:"
rownames(labortablerural)[13] <- "District"
rownames(labortablerural)[14] <- "State-month"

@@

labor3month <- cbind(labor3month, yield4monthly[-c(15:19),2])

# Table
colnames(labor3month) <- c("Farm", "Non-farm", "Yield")
kable(
      labor3month, caption = "Heterogeneity by month",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in column one is farm labor, the outcome is column two is non-farm labor, and the outcome in column three is village-level productivity. The independent variable for labor is wind, while the IV approach above is still used for yield. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(c(2:4),width = "2.5cm") %>%
  row_spec(c(14), hline_after = TRUE) %>%
  row_spec(c(12), bold = TRUE) %>%
  add_header_above(c(" " = 1, "Labor" = 2, " " = 1)) %>%
  kable_classic_2()

@@

I perform a similar exercise with yield, the results of which are in Table \@ref(tab:labor3month). I include only the five months of the year that are used in the calculation of the yield estimates, or June through October. The results are again from two-stage least squares, with the F-statistics for each month presented at the bottom; monthly wind remains a strong predictor of pollution. Column one presents results without controls for weather while column two presents results with controls for weather; the differences in coefficients make clear how important the inclusion of weather is here.

@@

A final caveat about these month-specific results is that they do not take into account possible interactions between different months. For example, yield might respond strongly to average pollution in June and July, which would not be captured in Table \@ref(tab:labor3month).

@@

# Table
colnames(yield7ivdiffindiff) <- c("(1)", "(2)", "(3)")
rownames(yield7ivdiffindiff) <- c("Particulate matter", "(log PM 2.5)", 
                                  "PM 2.5 times Coal", "",
                                  "Weather", "Weather (expanded)",
                                  "Fixed effects:", "Year", "Village",
                                  "F (PM)", "F (PM times Coal)", "Observations")
kable(
      yield7ivdiffindiff, caption = "Agricultural productivity and pollution source",
      align = "ccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(c(2:4),width = "2cm") %>%
  row_spec(c(7), bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  kable_classic_2()

@@

data <- matrix(NA, nrow = 7, ncol = 3)
rownames(data) <- c("shapefile", "coal plants", "wind", "pollution", "agriculture", "weather", "labor")
colnames(data) <- c("source", "geographic coverage", "temporal coverage")
data[1,1] <- "Asher et al. (2021)"
data[2,1] <- "Global Energy Monitor"
data[3,1] <- "NCAR"
data[4,1] <- "Hammer et al. (2020)"
data[5,1] <- "Gangopadhya et al. (2022)"
data[6,1] <- "TerraClimate"
data[7,1] <- "National Sample Survey (NSS)"
data[1,2] <- "India"
data[2,2] <- "global"
data[3,2] <- "global"
data[4,2] <- "global"
data[5,2] <- "India"
data[6,2] <- "global"
data[7,2] <- "India"
data[1,3] <- " "
data[2,3] <- "yearly"
data[3,3] <- "daily"
data[4,3] <- "monthly"
data[5,3] <- "two seasons/year"
data[6,3] <- "monthly"
data[7,3] <- "daily interviews"

@@

plant1 <- ggplot() +
                theme_map() +
                geom_sf(data = india_shape2, fill = NA, lwd = 0.01) +
                geom_sf(data = plants1990, size = 0.75, color = "black") +
                labs(x = "lon",
                     y = "lat",
                     subtitle = "A. 1990")

plant2 <- ggplot() +
                theme_map() +
                geom_sf(data = india_shape2, fill = NA, lwd = 0.01) +
                geom_sf(data = plants2010, size = 0.75, color = "black") +
                labs(x = "lon",
                     y = "lat",
                     subtitle = "B. 2010")

@@

p1 <- ggplot() + 
        theme_map() +
        geom_sf(data = india_shape, fill = NA) +
        geom_tile(data = windexample, aes(x = x, y = y, fill = wind_example), alpha = 0.3) +
        scale_fill_viridis_c("wind direction\n(degrees)", option = "viridis") +
        geom_sf(data = plants2010, size = 0.5) +
        labs(x = "lon",
             y = "lat",
             subtitle = "A. Wind direction") +
        theme(legend.position = c(0.6, 0.05),
              legend.direction = "vertical",
              legend.key.height = unit(0.4, 'cm'),
              legend.text = element_text(size = 8),
              legend.background=element_blank() )

p2 <- ggplot() + 
        theme_map() +
        geom_sf(data = districts, fill = NA) +
        geom_sf(data = villages %>% filter(is.na(days_sum)==F), aes(fill = days_sum), lwd = NA) +
        scale_fill_viridis_c("exposure (days)", option = "viridis") +
        labs(x = "lon",
             y = "lat",
             subtitle = "B. Aggregation to district") +
        theme(legend.position = c(0.5, 0.05),
              legend.direction = "horizontal",
              legend.key.width = unit(0.3, 'cm'),
              legend.text = element_text(size = 8),
              legend.background=element_blank() )

@@
